\documentclass[../main.tex]{subfiles}

\begin{document}

\begin{appendices}
\chapter{CMP variables description}
\label{appendix:MpDatasetTranslation}

This is a one to one copy of \textcite{polalehmannManifestoProjectDataset2024}, only the "Meaning" column has been added for better readablilty.

\begin{tiny}
\begin{longtable}{p{0.05\textwidth}|p{0.27\textwidth}|p{0.36\textwidth}}
\caption{CMP variables description} \label{tab:MpDatasetTranslation} \\
\hline 
\textbf{Code} & \textbf{Meaning} & \textbf{Description} \\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline 
\textbf{Code} & \textbf{Meaning} & \textbf{Description} \\ \hline 
\endhead

\hline \multicolumn{3}{|r|}{{Continued on next page}} \\ \hline
\endfoot

\hline \hline
\endlastfoot
per101 & Foreign\_Special\_Relationships\_Positive & Favourable mentions of particular countries with which the manifesto country has a special relationship; the need for co-operation with and/or aid to such countries. \\
per102 & Foreign\_Special\_Relationships\_Negative & Negative mentions of particular countries with which the manifesto country has a special relationship. \\
per103 & Anti-Imperialism & Negative references to imperial behaviour and/or negative references to one state exerting strong influence (political, military or commercial) over other states. May also include: • Negative references to controlling other countries as if they were part of an empire; • Favourable references to greater self-government and independence for colonies; • Favourable mentions of de-colonisation. \\
per104 & Military\_Positive & The importance of external security and defence. May include statements concerning: • The need to maintain or increase military expenditure; • The need to secure adequate manpower in the military; • The need to modernise armed forces and improve military strength; • The need for rearmament and self-defence; • The need to keep military treaty obligations. \\
per105 & Military\_Negative & Negative references to the military or use of military power to solve conflicts. References to the 'evils of war'. May include references to: • Decreasing military expenditures; • Disarmament; • Reduced or abolished conscription. \\
per106 & Peace & Any declaration of belief in peace and peaceful means of solving crises – absent reference to the military. May include: • Peace as a general goal; • Desirability of countries joining in negotiations with hostile countries; • Ending wars in order to establish peace. \\
per107 & Internationalism\_Positive & Need for international co-operation, including co-operation with specific countries other than those coded in 101. May also include references to the: • Need for aid to developing countries; • Need for world planning of resources; • Support for global governance; • Need for international courts; • Support for UN or other international organisations. \\
per108 & European\_Community/Union\_Positive & Favourable mentions of European Community/Union in general. May include the: • Desirability of the manifesto country joining (or remaining a member); • Desirability of expanding the European Community/Union; • Desirability of increasing the ECs/EUs competences; • Desirability of expanding the competences of the European Parliament. \\
per109 & Internationalism\_Negative & Negative references to international co-operation. Favourable mentions of national independence and sovereignty with regard to the manifesto country’s foreign policy, isolation and/or unilateralism as opposed to internationalism. \\
per110 & European\_Community/Union\_Negative & Negative references to the European Community/Union. May include: • Opposition to specific European policies which are preferred by European authorities; • Opposition to the net-contribution of the manifesto country to the EU budget. \\
per201 & Freedom\_and\_Human\_Rights & Favourable mentions of importance of personal freedom and civil rights in the manifesto and other countries. May include mentions of: • The right to the freedom of speech, press, assembly etc.; • Freedom from state coercion in the political and economic spheres; • Freedom from bureaucratic control; • The idea of individualism. \\
per202 & Democracy & Favourable mentions of democracy as the “only game in town”. General support for the manifesto country’s democracy. May also include: • Democracy as method or goal in national, international or other organisations (e.g. labour unions, political parties etc.); • The need for the involvement of all citizens in political decision making; • Support for either direct or representative democracy; • Support for parts of democratic regimes (rule of law, division of powers, independence of courts etc.). \\
per203 & Constitutionalism\_Positive & Support for maintaining the status quo of the constitution. Support for specific aspects of the manifesto country’s constitution. The use of constitutionalism as an argument for any policy. \\
per204 & Constitutionalism\_Negative & Opposition to the entirety or specific aspects of the manifesto country’s constitution. Calls for constitutional amendments or changes. May include calls to abolish or rewrite the current constitution. \\
per301 & Decentralization & Support for federalism or decentralisation of political and/or economic power. May include: • Favourable mentions of the territorial subsidiary principle; • More autonomy for any sub-national level in policy making and/or economics, including municipalities; • Support for the continuation and importance of local and regional customs and symbols and/or deference to local expertise; • Favourable mentions of special consideration for sub-national areas. \\
per302 & Centralisation & General opposition to political decision-making at lower political levels. Support for unitary government and for more centralisation in political and administrative procedures. \\
per303 & Governmental\_and\_Administrative\_Efficiency & Need for efficiency and economy in government and administration and/or the general appeal to make the process of government and administration cheaper and more efficient. May include: • Restructuring the civil service; • Cutting down on the civil service; • Improving bureaucratic procedures. \\
per304 & Political\_Corruption & Need to eliminate political corruption and associated abuses of political and/or bureaucratic power. Need to abolish clientelist structures and practices. \\
per305 & Political\_Authority & References to the manifesto party’s competence to govern and/or other party’s lack of such competence. Also includes favourable mentions of the desirability of a strong and/or stable government in general. \\
per401 & Free\_Market\_Economy & Favourable mentions of the free market and free market capitalism as an economic model. May include favourable references to: • Laissez-faire economy; • Superiority of individual enterprise over state and control systems; • Private property rights; • Personal enterprise and initiative; • Need for unhampered individual enterprises. \\
per402 & Incentives\_Positive & Favourable mentions of supply side oriented economic policies (assistance to businesses rather than consumers). May include: • Financial and other incentives such as subsidies, tax breaks etc.; • Wage and tax policies to induce enterprise; • Encouragement to start enterprises. \\
per403 & Market\_Regulation & Support for policies designed to create a fair and open economic market. May include: • Calls for increased consumer protection; • Increasing economic competition by preventing monopolies and other actions disrupting the functioning of the market; • Defence of small businesses against disruptive powers of big businesses; • Social market economy. \\
per404 & Economic\_Planning & Favourable mentions of long-standing economic planning by the government. May be: • Policy plans, strategies, policy patterns etc.; • Of a consultative or indicative nature. \\
per405 & Corporatism/Mixed\_Economy & Favourable mentions of cooperation of government, employers, and trade unions simultaneously. The collaboration of employers and employee organisations in overall economic planning supervised by the state. \\
per406 & Protectionism\_Positive & Favourable mentions of extending or maintaining the protection of internal markets (by the manifesto or other countries). Measures may include: • Tariffs; • Quota restrictions; • Export subsidies. \\
per407 & Protectionism\_Negative & Support for the concept of free trade and open markets. Call for abolishing all means of market protection (in the manifesto or any other country). \\
per408 & Economic\_Goals & Broad and general economic goals that are not mentioned in relation to any other category. General economic statements that fail to include any specific goal. \\
per409 & Keynesian\_Demand\_Management & Favourable mentions of demand side oriented economic policies (assistance to consumers rather than businesses). Particularly includes increase private demand through • Increasing public demand; • Increasing social expenditures. May also include: • Stabilisation in the face of depression; • Government stimulus plans in the face of economic crises. \\
per410 & Economic\_Growth\_Positive & The paradigm of economic growth. Includes: • General need to encourage or facilitate greater production; • Need for the government to take measures to aid economic growth. \\
per411 & Technology\_and\_Infrastructure\_Positive & Importance of modernisation of industry and updated methods of transport and communication. May include: • Importance of science and technological developments in industry; • Need for training and research within the economy (This does not imply education in general (see category 506); • Calls for public spending on infrastructure such as roads and bridges; • Support for public spending on technological infrastructure (e.g.: broadband internet, etc.). \\
per412 & Controlled\_Economy & Support for direct government control of economy. May include, for instance: • Control over prices; • Introduction of minimum wages. \\
per413 & Nationalisation & Favourable mentions of government ownership of industries, either partial or complete; calls for keeping nationalised industries in state hand or nationalising currently private industries. May also include favourable mentions of government ownership of land. \\
per414 & Economic\_Orthodoxy & Need for economically healthy government policy making. May include calls for: • Reduction of budget deficits; • Retrenchment in crisis; • Thrift and savings in the face of economic hardship; • Support for traditional economic institutions such as stock market and banking system; • Support for strong currency. \\
per415 & Marxist\_Analysis & Positive references to Marxist-Leninist ideology and specific use of Marxist-Leninist terminology by the manifesto party (typically but not necessary by communist parties). \\
per416 & Anti-Growth\_Economy\_Positive & Favourable mentions of anti-growth politics. Rejection of the idea that all growth is good growth. Opposition to growth that causes environmental or societal harm. Call for sustainable economic development. \\
per501 & Environmental\_Protection & General policies in favour of protecting the environment, fighting climate change, and other “green” policies. For instance: • General preservation of natural resources; • Preservation of countryside, forests, etc.; • Protection of national parks; • Animal rights. May include a great variance of policies that have the unified goal of environmental protection. \\
per502 & Culture\_Positive & Need for state funding of cultural and leisure facilities including arts and sport. May include: • The need to fund museums, art galleries, libraries etc.; • The need to encourage cultural mass media and worthwhile leisure activities, such as public sport clubs. \\
per503 & Equality\_Positive & Concept of social justice and the need for fair treatment of all people. This may include: • Special protection for underprivileged social groups; • Removal of class barriers; • Need for fair distribution of resources; • The end of discrimination (e.g. racial or sexual discrimination). \\
per504 & Welfare\_State\_Expansion & Favourable mentions of need to introduce, maintain or expand any public social service or social security scheme. This includes, for example, government funding of: • Health care • Child care • Elder care and pensions • Social housing \\
per505 & Welfare\_State\_Limitation & Limiting state expenditures on social services or social security. Favourable mentions of the social subsidiary principle (i.e. private care before state care); \\
per506 & Education\_Expansion & Need to expand and/or improve educational provision at all levels. \\
per507 & Education\_Limitation & Limiting state expenditure on education. May include: • The introduction or expansion of study fees at all educational levels • Increasing the number of private schools. \\
per601 & National\_Way\_of\_Life\_Positive & Favourable mentions of the manifesto country’s nation, history, and general appeals. May include: • Support for established national ideas; • General appeals to pride of citizenship; • Appeals to patriotism; • Appeals to nationalism; • Suspension of some freedoms in order to protect the state against subversion. \\
per602 & National\_Way\_of\_Life\_Negative & Unfavourable mentions of the manifesto country’s nation and history. May include: • Opposition to patriotism; • Opposition to nationalism; • Opposition to the existing national state, national pride, and national ideas. \\
per603 & Traditional\_Morality\_Positive & Favourable mentions of traditional and/or religious moral values. May include: • Prohibition, censorship and suppression of immorality and unseemly behaviour; • Maintenance and stability of the traditional family as a value; • Support for the role of religious institutions in state and society. \\
per604 & Traditional\_Morality\_Negative & Opposition to traditional and/or religious moral values. May include: • Support for divorce, abortion etc.; • General support for modern family composition; • Calls for the separation of church and state. \\
per605 & Law\_and\_Order\_Positive & Favourable mentions of strict law enforcement, and tougher actions against domestic crime. Only refers to the enforcement of the status quo of the manifesto country’s law code. May include: • Increasing support and resources for the police; • Tougher attitudes in courts; • Importance of internal security. \\
per606 & Civic\_Mindedness\_Positive & Appeals for national solidarity and the need for society to see itself as united. Calls for solidarity with and help for fellow people, familiar and unfamiliar. May include: • Favourable mention of the civil society; • Decrying anti-social attitudes in times of crisis; • Appeal for public spiritedness; • Support for the public interest. \\
per607 & Multiculturalism\_Positive & Favourable mentions of cultural diversity and cultural plurality within domestic societies. May include the preservation of autonomy of religious, linguistic heritages within the country including special educational provisions. \\
per608 & Multiculturalism\_Negative & The enforcement or encouragement of cultural integration. Appeals for cultural homogeneity in society. \\
per701 & Labour\_Groups\_Positive & Favourable references to all labour groups, the working class, and unemployed workers in general. Support for trade unions and calls for the good treatment of all employees, including: • More jobs; • Good working conditions; • Fair wages; • Pension provisions etc. \\
per702 & Labour\_Groups\_Negative & Negative references to labour groups and trade unions. May focus specifically on the danger of unions 'abusing power'. \\
per703 & Agriculture\_and\_Farmers\_Positive & Specific policies in favour of agriculture and farmers. Includes all types of agriculture and farming practises. Only statements that have agriculture as the key goal should be included in this category. \\
per704 & Middle\_Class\_and\_Professional\_Groups & General favourable references to the middle class. Specifically, statements may include references to: • Professional groups, (e.g.: doctors or lawyers); • White collar groups, (e.g.: bankers or office employees), • Service sector groups (e.g.: IT industry employees); • Old and/or new middle class. \\
per705 & Underprivileged\_Minority\_Groups & Very general favourable references to underprivileged minorities who are defined neither in economic nor in demographic terms (e.g. the handicapped, homosexuals, immigrants, indigenous). Only includes favourable statements that cannot be classified in other categories (e.g. 503, 504, 604, 607 etc.) \\
per706 & Non-economic\_Demographic\_Groups & General favourable mentions of demographically defined special interest groups of all kinds. They may include: • Women; • University students; • Old, young, or middle aged people. Might include references to assistance to these groups, but only if these do not fall under other categories (e.g. 503 or 504). \\
per1011 & Russia/USSR/CIS\_Positive & Favourable mentions of Russia, the USSR, the CMEA bloc or the Community of Independent States. \\
per1012 & Western\_States\_Positive & Favourable mentions of Western states, including the USA and Germany. \\
per1013 & Eastern\_European\_Countries\_Positive & Favourable mentions of Eastern European countries in general. \\
per1014 & Baltic\_States\_Positive & Favourable mentions of the Baltic states, including other states bordering the Baltic Sea. \\
per1015 & Nordic\_Council\_Positive & Favourable mentions of the Nordic Council. \\
per1016 & SFR\_Yugoslavia\_Positive & Favourable mentions of countries formerly belonging to SFR Yugoslavia including special relationships with Montenegro, Macedonia, Slovenia, Croatia and Bosnia-Hercegovina. \\
per1021 & Russia/USSR/CIS\_Negative & Negative mentions of Russia, the USSR or the Community of Independent States. \\
per1022 & Western\_States\_Negative & Negative mentions of Western states, including the USA and Germany. \\
per1023 & East\_European\_Countries\_Negative & Negative mentions of Eastern European countries in general. \\
per1024 & Baltic\_States\_Negative & Negative references to the Baltic states. \\
per1025 & Nordic\_Council\_Negative & Negative references to the Nordic Council. \\
per1026 & SFR\_Yugoslavia\_Negative & Negative mentions of countries formerly belonging to SFR Yugoslavia including negative references to Montenegro, Macedonia, Slovenia, Croatia and Bosnia-Hercegovina. \\
per1031 & Russian\_Army\_Negative & Need to withdraw the Russian army from the territory of the manifesto country; need to receive reparations for the damage caused by the Russian army or other Soviet institutions. \\
per1032 & Independence\_Positive & Favourable mentions of the independence and sovereignty of the manifesto country. \\
per1033 & Rights\_of\_Nations\_Positive & Favourable mentions of freedom, rights and interests of nations. \\
per2021 & Transition\_to\_Democracy & General references to the transition process of one-party states to pluralist democracy. \\
per2022 & Restrictive\_Citizenship\_Positive & Favourable mentions of restrictions in citizenship; restrictions in enfranchisement with respect to (ethnic) groups. \\
per2023 & Lax\_Citizenship\_Positive & Favourable mentions of lax citizenship and election laws; no or few restrictions in enfranchisement. \\
per2031 & Presidential\_Regime\_Positive & Support for current presidential regime; statements in favour of a powerful presidency. \\
per2032 & Republic\_Positive & Support for the republican form of government as opposed to monarchy. \\
per2033 & Checks\_and\_Balances\_Positive & Support for checks and balances and separation of powers, and specifically for limiting the powers of the presidency by increasing legislative/judicial powers, or transferring some executive powers to the legislature or judiciary. \\
per2041 & Monarchy\_Positive & Support for a monarchy, including conceptions of constitutional monarchy. \\
per3011 & Republican\_Powers\_Positive & Favourable mentions of stronger republican powers. \\
per3051 & Public\_Situation\_Negative & Negative references to the situation in public life after the founding elections. \\
per3052 & Communist\_Positive & Co-operation with former authorities/communists in the transition period; pro-communist involvement in the transition process; and 'let sleeping dogs lie' in dealing with the nomenclature. \\
per3053 & Communist\_Negative & Against communist involvement in democratic government; weeding out the collaborators from governmental service; need for political coalition except communist parties. \\
per3054 & Rehabilitation\_and\_Compensation\_Positive & References to civic rehabilitation of politically persecuted people in the communist era; references to juridical compensation concerning communist expropriations; moral compensation. \\
per3055 & Political\_Coalitions\_Positive & Positive references to the need of broader political coalition; need for co-operation at the political level; necessity of collaboration among all political forces. \\
per4011 & Privatisation\_Positive & Favourable references to privatisation. \\
per4012 & Control\_of\_Economy\_Negative & Negative references to the general need for direct governmental control of the economy. \\
per4013 & Property-Restitution\_Positive & Favourable references to the physical restitution of property to previous owners. \\
per4014 & Privatisation\_Vouchers\_Positive & Favourable references to privatisation vouchers. \\
per4121 & Social\_Ownership\_Positive & Favourable references to the creation or preservation of co-operative or non-state social ownership within a market economy. \\
per4122 & Mixed\_Economy\_Positive & Favourable references to mixed ownership within a market economy. \\
per4123 & Publicly-Owned\_Industry\_Positive & Positive references to the concept of publicly-owned industries. \\
per4124 & Socialist\_Property\_Positive & Positive references to socialist property, including public and co-operative property; negative references to privatisation. \\
per4131 & Property-Restitution\_Negative & Negative references to the physical restitution of property to previous owners. \\
per4132 & Privatisation\_Negative & Negative references to the privatisation system; need to change the privatisation system. \\
per5021 & Private-Public\_Mix\_in\_Culture\_Positive & Necessity of private provisions due to economic constraints; private funding in addition to public activity. \\
per5031 & Private-Public\_Mix\_in\_Social\_Justice\_Positive & Necessity of private initiatives due to economic constraints. \\
per5041 & Private-Public\_Mix\_in\_Welfare\_Positive & Necessity of private welfare provisions due to economic constraints; desirability of competition in welfare service provisions; private funding in addition to public activity. \\
per5061 & Private-Public\_Mix\_in\_Education\_Positive & Necessity of private education due to economic constraints; desirability of competition in education. \\
per6011 & The\_Karabakh\_Issue\_Positive & Positive references to the unity of Karabakh and Armenia or the recognition of the independent Republic of Karabakh; rendering assistance to Karabakh. \\
per6012 & Rebuilding\_the\_USSR\_Positive & Favourable mentions of the reunification of all republics and nations living on the former territory of the USSR into a new common (democratic) state or into a common economic space whereby the new union would be the guarantor of the manifesto country’s sovereignty; negative references to the dissolution of the USSR and the respective treaties. \\
per6013 & National\_Security\_Positive & Support for or need to maintain national security in all spheres of social life; policies devoted to this goal. \\
per6014 & Cyprus\_Issue & All references concerning the division of Cyprus in a Greek and a Turkish part. \\
per6061 & General\_Crisis & Identification of a general crisis in the country. \\
per6071 & Cultural\_Autonomy\_Positive & Favourable mentions of cultural autonomy. \\
per6072 & Multiculturalism\_pro\_Roma\_Positive & Favourable mentions of cultural autonomy of Roma. \\
per6081 & Multiculturalism\_pro\_Roma\_Negative & Negative mentions of cultural autonomy of Roma. \\
per7051 & Minorities\_Inland\_Positive & References to manifesto country minorities in foreign countries; positive references to manifesto country minorities. \\
per7052 & Minorities\_Abroad\_Positive & References to ethnic minorities living in the manifesto country such as Latvians living in Estonia. \\
per7061 & War\_Participants\_Positive & Favourable mentions of, or need for, assistance to people taking part in the war on the territory of ex-Yugoslavia. \\
per7062 & Refugees\_Positive & Favourable mentions of, or need for, assistance to people who left their homes because of the war (for instance, on the territory of ex-Yugoslavia) or were forcibly displaced. \\
per103\_1 & Anti-Imperialism\_State\_Centred\_Anti-Imperialism & Negative references to imperial behaviour and/or negative references to one state exerting strong influence (political, military or commercial) over other states. May also include: • Negative references to controlling other countries as if they were part of an empire; • Favourable references to greater self-government and independence for colonies; • Favourable mentions of de-colonisation. \\
per103\_2 & Anti-Imperialism\_Foreign\_Financial\_Influence & Negative references and statements against international financial organisations or states using monetary means to assert strong influence over the manifesto country or other states. May include: • Statements against the World Bank, IMF etc.; • Statements against the Washington Consensus; • Statements against foreign debt circumscribing state actions. \\
per201\_1 & Freedom & Favourable mentions of importance of personal freedom in the manifesto and other countries. May include mentions of: • Freedom from state coercion in the political and economic spheres; • Freedom from bureaucratic control; • The idea of individualism \\
per201\_2 & Human\_Rights & Favourable mentions of importance of human and civil rights in the manifesto and other countries, including the right to freedom of speech, press, assembly etc.; supportive refugee policies. \\
per202\_1 & Democracy\_General\_Positive & Favourable mentions of democracy as the “only game in town”. General support for the manifesto country’s democracy. May also include: • Democracy as method or goal in national, international or other organisations (e.g. labour unions, political parties etc.); • The need for the involvement of all citizens in political decision making; • Support for parts of democratic regimes (rule of law, division of powers, independence of courts etc.). \\
per202\_2 & Democracy\_General\_Negative & Statements against the idea of democracy, in general or in the manifesto country. Calls for reducing or withholding democratic rights from all or certain groups of people. Calls for the introduction or maintaining of a non-democratic regime, e.g. monarchy or rule of the military. \\
per202\_3 & Representative\_Democracy\_Positive & Favourable mentions of the system of representative democracy, in particular in contrast to direct democracy. This includes the protection of representative institutions and actors against direct democratic elements. \\
per202\_4 & Direct\_Democracy\_Positive & Favourable mentions of the system of direct democracy, in particular in contrast to representative democracy. This includes the call for the introduction and/or extension of referenda, participatory budgets and other forms of direct democracy. \\
per305\_1 & Political\_Authority\_Party\_Competence & References to the manifesto party’s competence to govern and/or other party’s lack of such competence. \\
per305\_2 & Political\_Authority\_Personal\_Competence & Reference to the presidential candidate’s or party leader’s personal competence to govern and/or other candidate’s or leader’s lack of such competence. \\
per305\_3 & Political\_Authority\_Strong\_government & Favourable mentions of the desirability of a strong and/or stable government in general. \\
per305\_4 & Transition\_Pre-Democratic\_Elites\_Positive & Co-operation with pre-democratic authorities in the transition period; amnesty for former, non-Democratic elites; and ''let sleeping dogs lie'' in dealing with the nomenclature of the former, non-Democratic regime. \\
per305\_5 & Transition\_Pre-Democratic\_Elites\_Negative & Against pre-democratic elite’s involvement in democratic government; weeding out the collaborators of former, non-Democratic regime from governmental service; for truth commissions and other institutions illuminating recent history. \\
per305\_6 & Transition\_Rehabilitation\_and\_Compensation & References to civic rehabilitation of politically persecuted people in the authoritarian era; references to juridical compensation concerning authoritarian expropriations; moral compensation. \\
per416\_1 & Anti-Growth\_Economy\_Positive\_New & Favourable mentions of anti-growth politics. Rejection of the idea that growth is good. \\
per416\_2 & Sustainability\_Positive & Call for sustainable economic development. Opposition to growth that causes environmental or societal harm. \\
per601\_1 & National\_Way\_of\_Life\_General\_Positive & Favourable mentions of the manifesto country’s nation, history, and general appeals. May include: • Support for established national ideas; • General appeals to pride of citizenship; • Appeals to patriotism; • Appeals to nationalism; • Suspension of some freedoms in order to protect the state against subversion. \\
per601\_2 & National\_Way\_of\_Life\_Immigration\_Negative & Statement advocating the restriction of the process of immigration, i.e. accepting new immigrants. Might include statements regarding: • Immigration being a threat to national character of the manifesto country; • 'the boat is full' argument; • The introduction of migration quotas, including restricting immigration from specific countries or regions etc. \\
per602\_1 & National\_Way\_of\_Life\_General\_Negative & Unfavourable mentions of the manifesto country’s nation and history. May include: • Opposition to patriotism; • Opposition to nationalism; • Opposition to the existing national state, national pride, and national ideas. \\
per602\_2 & National\_Way\_of\_Life\_Immigration\_Positive & Statements favouring new immigrants; against restrictions and quotas; rejection of the 'boat is full' argument. Includes allowing new immigrants for the benefit of the manifesto country’s economy. \\
per605\_1 & Law\_and\_Order\_Positive\_New & Favourable mentions of strict law enforcement, and tougher actions against domestic crime. Only refers to the enforcement of the status quo of the manifesto country’s law code. May include: • Increasing support and resources for the police; • Tougher attitudes in courts; • Importance of internal security. \\
per605\_2 & Law\_and\_Order\_Negative\_New & Favourable mentions of less law enforcement or rejection of plans for stronger law enforcement. Only refers to the enforcement of the status quo of the manifesto country’s law code. May include: • Less resources for police; • Reducing penalties; • Calls for abolishing the death penalty; • Decriminalisation of drugs, prostitution etc. \\
per606\_1 & Civic\_Mindedness\_General\_Positive & General appeals for national solidarity and the need for society to see itself as united. Calls for solidarity with and help for fellow people, familiar and unfamiliar. May include: • Favourable mention of the civil society and volunteering; • Decrying anti-social attitudes in times of crisis; • Appeal for public spiritedness; • Support for the public interest. \\
per606\_2 & Civic\_Mindedness\_Bottom-Up\_Activisim & Appeals to grassroots movements of social change; banding all sections of society together to overcome common adversity and hardship; appeals to the people as a united actor. \\
per607\_1 & Multiculturalism\_General\_Positive & Favourable mentions of cultural diversity and cultural plurality within domestic societies. May include the preservation of autonomy of religious, linguistic heritages within the country including special educational provisions. \\
per607\_2 & Multiculturalism\_Immigrants\_Diversity & Statements favouring the idea that immigrants keep their cultural traits; voluntary integration; state providing opportunities to integrate. \\
per607\_3 & Multiculturalism\_Indigenous\_rights\_Positive & Calls for the protection of indigenous people, strengthening their rights, may include: • Protection of their lands; • Introduction of special provisions in the democratic or bureaucratic process; • Compensation for past grief. \\
per608\_1 & Multiculturalism\_General\_Negative & The enforcement or encouragement of cultural integration. Appeals for cultural homogeneity in society. \\
per608\_2 & Multiculturalism\_Immigrants\_Assimilation & Calls for immigrants that are in the country to adopt the manifesto country’s culture and fully assimilate. Reinforce integration. \\
per608\_3 & Multiculturalism\_Indigenous\_rights\_Negative & Rejection of idea of special protection for indigenous people. \\
per703\_1 & Agriculture\_and\_Farmers\_Positive\_New & Specific policies in favour of agriculture and farmers. Includes all types of agriculture and farming practises. Only statements that have agriculture as the key goal should be included in this category. \\
per703\_2 & Agriculture\_and\_Farmers\_Negative\_New & Rejection of policies favouring agriculture and farmers. May include: • Cap or abolish subsidies; • Reject special welfare provisions for farmers. \\
rile & Right\_Left &  Right-left position of party as given in Michael Laver/Ian Budge (eds.): Party Policy and Government Coalitions, Houndmills, Basingstoke, Hampshire: The MacMillan Press 1992: (per104 + per201 + per203 + per305 + per401 + per402 + per407 + per414 + per505 + per601 + per603 + per605 + per606)- (per103 + per105 + per106 + per107 + per403 + per404 + per406 + per412 + per413 + per504 + per506 + per701 + per202) \\
planeco & Planet\_eco & per403 + per404 + per412 \\
markeco & Mark\_eco & per401 + per414 \\
welfare & Welfare & per503 + per504 \\
intpeace & Int\_Peace & per102 + per105 + per106
\end{longtable}
\end{tiny}

\end{appendices}

\end{document}